Causal.jl: A Modeling and Simulation Framework for Causal Models

### 2022-01-29 paper/header.tex
Removed backslashes from the paper.yml file.

\title{Causal.jl:\\A Modeling and Simulation Framework for Causal Models}

@@

\hypersetup{
pdftitle = {Causal.jl:\\A Modeling and Simulation Framework for Causal Models},
pdfsubject = {JuliaCon 2019 Proceedings},
pdfauthor = {Zekeriya Sarı, Serkan Günel},
pdfkeywords = {System Modeling, Causal Modeling, System Simulation, Dynamical Systems, Julia Programming Language},
}

>>>>

\title{Causal.jl: A Modeling and Simulation Framework for Causal Models}

@@

\hypersetup{
pdftitle = {Causal.jl: A Modeling and Simulation Framework for Causal Models},
pdfsubject = {JuliaCon 2019 Proceedings},
pdfauthor = {Zekeriya Sarı, Serkan Günel},
pdfkeywords = {System Modeling, Causal Modeling, System Simulation, Dynamical Systems, Julia Programming Language},
}
